Data Science Final Project

### 2022-05-30 code.Rmd
update writeup

---
title: "R Notebook"
output: html_notebook
---

@@

---OUR PLAN---

Response variable: soldPrice (price at which the house was sold)

Possible predictors:
- nbhd (neighborhood)
- bed (number of bedrooms)
- fullBath (number of full baths)
- halfBath (number of half baths)
- style (style)
- age (yearSold minus yearBuilt)
- originalPrice (original price)
- lastPrice (price at which the house was last sold)
- marketDays (days the house was on market)
- yearSold, daySold, monthSold (date at which the house was sold)

Regression methods we will use: 
- full linear model (lm)
- subset selection (forward, backward)
- ridge (ridge)
- lasso (lasso)
- elastic net (ela)
- principal components regression (pcr)

>>>>

---
title: "R Notebook"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

@@

### 2022-05-30 paper-writeup.Rmd
update writeup

>>>>

# Introduction

---OUR PLAN---

Response variable: soldPrice (price at which the house was sold)

Possible predictors:

- nbhd (neighborhood) 
- bed (number of bedrooms) 
- fullBath (number of full baths) 
- halfBath (number of half baths) 
- style (style) 
- age (yearSold minus yearBuilt) 
- originalPrice (original price) 
- lastPrice (price at which the house was last sold) 
- marketDays (days the house was on market) 
- yearSold, daySold, monthSold (date at which the house was sold)

Regression methods we will use:

- full linear model (lm) 
- subset selection (forward, backward) 
- ridge (ridge) 
- lasso (lasso) 
- elastic net (ela) 
- principal components regression (pcr)

# Regression Analysis

Our final models are Lasso and PCR. Lasso has the lowest variance, while PCR has the highest R2.

# Discussion and Limitations

Assumptions possibly not met, curse of dimensionality, did not incorporate census data

# Conclusion

# Additional Work

Introduce the other models we tried
